Analyzing X-ray images in Python with scikit-image

### 2016-08-20 skimage_tomo.tex
Add suggestions for overview section

In this section, we provide a short overview of the typical use patterns of
\texttt{scikit-image}, illutrated by short snippets of code. Indeed, since
Python is a programming language, the user interacts with data objects and
images through code, which is either typed and executed in an interactive
interpreter, or written in text files (scripts) that are executed.

@@

Images are manipulated as numerical arrays of uniform
data type, a format that guarantees a fast access to the computer memory. The
n-dimensional (2-D, 3-D, \dots) numerical array object is provided by the
\texttt{NumPy} module \citep{Vanderwalt2011}.

In image processing, one of the first tasks is therefore to generate
\texttt{NumPy} arrays, which is often done by reading data from files. We
read one 2-D image from a file and display it with the following lines of code:

@@

\texttt{skimage} is the name under which \texttt{scikit-image} is imported in
Python code. Note that functions (such as \texttt{imread} to read an image
file, or \texttt{imshow} to display an image) are found in thematic submodules of
\texttt{skimage}, such as \texttt{io} for Input/Output.

A stack of 2-D images, such as tomography slices generated by a reconstruction algorithm, can be opened as an image collection or a 3-D array:
\lstinputlisting[language=Python]{io_coll.py}
Raw data formats can be opened using the \texttt{NumPy} functions \texttt{fromfile} or \texttt{memmap}, and \texttt{hdf5} files are opened using modules such as \texttt{h5py} or \texttt{pytables}.

\texttt{scikit-image} has a very simple Application Programming Interface
(API), based almost only on
functions. Most functions take an image (\emph{i.e} a multi-dimensional
array) as input parameter:
\begin{lstlisting}
>>> from skimage import filters
>>> im_gaussian = filters.gaussian(im)
\end{lstlisting}

Optional parameters can be passed as Python's \emph{keyword arguments},
in addition to the image parameter.
\begin{lstlisting}
>>> im_gaussian = filters.gaussian(im, sigma=3, mode='wrap')
\end{lstlisting}
A few functions require several arrays to be passed, such as the
watershed segmentation algorithm that takes as parameters the image to be
segmented, and an image of markers from which labels are propagated:
\begin{lstlisting}
>>> from skimage import morphology
>>> labels = morphology.watershed(im, markers)
\end{lstlisting}
Therefore, the image processing workflow can be considered as a directed graph
(a richer structure than a linear pipeline), where nodes are image-shaped arrays, and
edges are functions of \texttt{scikit-image} transforming the arrays (see
Fig.~\ref{fig:ecosystem}).

Most functions take indifferently 2-D or 3-D images as arguments, so that
the same functions can be used to process tomography and microscopy
images. Only a few functions do not support 3-D images and raise an error
when passed a 3-D argument:
\begin{lstlisting}
>>> filters.prewitt(im)
[...]
ValueError: The parameter `image` must be a 2-dimensional array
\end{lstlisting}

Another type of functions returns numerical value(s) that do not
correspond to image objects, such as pixel coordinates of objects of
interest or statistical
information about the image:
\begin{lstlisting}
>>> from skimage import exposure
>>> counts, bins = exposure.histogram(im)
>>> counts.shape
(256,)
\end{lstlisting}

>>>>

In this section, we provide a short overview of the typical use patterns of
\texttt{scikit-image}, illutrated by short snippets of code. Since
Python is a programming language, the user interacts with data objects and
images through code, which is either entered and executed in an interactive
interpreter, or written in text files (so-called scripts) that are executed.

@@

Images are manipulated as numerical arrays, each with a single, uniform
data type.  This common format guarantees interoperability with other
libraries and straightforward access to and interpretation of computer memory. The
N-dimensional (2-D, 3-D, \dots) numerical array object is provided by the
\texttt{NumPy} module \citep{Vanderwalt2011}.

In image processing in Python, one of the first tasks then is to generate
\texttt{NumPy} arrays, which is often achieved by reading data from files. We
read one 2-dimensional image from a file and display it as follows:

@@

\texttt{skimage} is the name under which \texttt{scikit-image} is imported in
Python code. Note that functions (such as \texttt{imread} that reads an image
file, or \texttt{imshow} that displays an image) are found in thematic submodules of
\texttt{skimage}, such as \texttt{io} for Input/Output.

A stack of 2-D images, such as tomography slices generated by a reconstruction algorithm, can be opened as an image collection or a 3-D array:
\lstinputlisting[language=Python]{io_coll.py}
Raw data formats can be opened using the \texttt{NumPy} functions \texttt{fromfile} or \texttt{memmap}, and \texttt{hdf5} files are accessed using modules such as \texttt{h5py}, \texttt{pytables}.

\texttt{scikit-image} has a very simple Application Programming Interface
(API), based almost exclusively on
functions. Most functions take an image (\emph{i.e} a multi-dimensional
array) as input parameter:
\begin{lstlisting}
>>> from skimage import filters
>>> im_gaussian = filters.gaussian(im)
\end{lstlisting}

Optional parameters can be passed as Python \emph{keyword arguments},
in addition to the image parameter.
\begin{lstlisting}
>>> im_gaussian = filters.gaussian(im, sigma=3, mode='wrap')
\end{lstlisting}
A few functions require several arrays to be passed, such as the
watershed segmentation algorithm that takes as parameters the image to be
segmented, and an image of markers from which labels are propagated:
\begin{lstlisting}
>>> from skimage import morphology
>>> labels = morphology.watershed(im, markers)
\end{lstlisting}
Therefore, the image processing workflow can be seen as a directed graph
(a richer structure than a linear pipeline), where nodes are image-shaped arrays, and
edges are functions of \texttt{scikit-image} transforming the arrays (see
Fig.~\ref{fig:ecosystem}).

Most functions take both 2-D and 3-D images as arguments, so that
the same functions can be used to process tomography and microscopy
images. The rest raise an error
when passed a 3-D argument:
\begin{lstlisting}
>>> filters.prewitt(im)
[...]
ValueError: The parameter `image` must be a 2-dimensional array
\end{lstlisting}

While the majority of functions return processed images, returns can
also be numerical value(s) such as pixel coordinates of objects of
interest or statistical
information about the image:
\begin{lstlisting}
>>> from skimage import exposure
>>> counts, bins = exposure.histogram(im)
>>> counts.shape
(256,)
\end{lstlisting}
